Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
really flimsy related work section

>>>>

Beyond discussions of simply applying priority tables, perhaps the most closely related work in the Aircraft EPS community focuses on optimizing \emph{the EPS topology itself}~\cite{Chandrasekaran:2003, VanDriel:2006, Pinto:2010}. 
In contrast to these results, we focus on optimizing the control of load shedding and generator assignment of any given EPS topology, while also preserving safety.
An other related direction is the work by Xu et al.~\cite{xu:2012}, who proposes correct-by-construction design of load management systems.
While the work in~\cite{xu:2012} guarantees safety, it doesn't optimize for minimal load shedding or other similar metrics.
